---
title: "Lists"
---

```{r setup}
library(tidyverse)
install.packages("repurrrsive")
library(repurrrsive)
library(broom)
names(sw_people) <- sw_people %>% map_chr("name")

```

# Lists

## Your Turn 1

Run the code below, which displays a list. What do you see?

```{r}
sw_people %>% head(3)
sw_people$`Luke Skywalker`
sw_people[[2]]
```

## Quiz

```{r}
vec <- c(-2, -1, 0)
lst <- list(-2, -1, 0)

abs(vec)
abs(lst)
```

## Your Turn 2

Who was taller Anakin Skywalker or Darth Vader? 
Use the RStudio Viewer to find the answer (in cm).

*Hint: View() sw_people*

```{r}
view(sw_people)

#after you view you can click on the info you want
```

## Your Turn 3

Here are two subsetting commands. Do they return the same values? Run the code chunks below to confirm.

```{r}
a_list <- list(num = c(8, 9), 
               log = TRUE,    
               cha = c("a", "b", "c"))
```

```{r}
a_list["num"]
#single bracket pulls name and info
```

```{r}
a_list[["num"]]
a_list$num #does same as above
#dbl bracket just pulls out info
```


Take Aways

* Use `View()` to inspect lists
* Use `[[ ]]`, or `$` to extract values from lists
* Lists can be a column in a data frame
* Tables are an organizational structure that you can manipulate.
